Maximising the guaranteed feasible set for stochastic MPC with chance constraints

### 2017-03-03 draft.tex
updated statement and proof of Theorem 2 after review

\title{Maximising the guaranteed feasible set for stochastic MPC with chance constraints}%\thanksref{footnoteinfo}} 
% Title, preferably not more than 10 words.

@@

\begin{keyword}                           % Five to ten keywords,  
Robust control; chance constraints;  invariant sets; stochastic MPC.
\end{keyword}                             % keyword list or with the 
                                          % help of the Automatica 
                                          % keyword wizard

@@

\vspace{0.5\baselineskip}
\begin{thm}\label{thm2}
Let $\Gamma$ be a matrix such that $\Gamma x\leq\bfa{1}$ and $-\Gamma x\leq\bfa{1}$ for all $x\in X_0$ and let $\bigl((A+BK),\Gamma\bigr)$ be observable, then the iteration~\eqref{eq:MRPI:sequence} %terminates after a finite number, $N$, of iterations, such that 
yields $X_{k+1}=X_k$ for all $k\geq N$ and hence $X_k=X^\infty$ for some finite integer $N$.
\end{thm}
%
The matrix~$\Gamma$ is an analytical object and can be made up of~$E_i$ and~$F_iK$, but does not need to contain all inequalities supporting~$X_0$, e.g. in asymmetrical cases.
%
\\[1em]
%
\bpf
%
The observability of the pair $\bigl((A+BK),\Gamma\bigr)$ implies that $X_{d-1}$ is compact, since 
\begin{align*}
X_{d-1} 
&\subseteq\bigcap_{k\leq d-1}(A+BK)^{-k} X_0\\
&\subseteq \Bigl\{x:\pm\Gamma x\leq\bfa{1}\wedge\dots\wedge\pm\Gamma(A+BK)^{d-1} x\leq\bfa{1} \Bigr\}\\
& = \bigl\{x:\pm\Gamma \Obs x\leq \bfa{1}\bigr\}
\end{align*}
where $\Obs$ is the (full rank) observability matrix.

Let~$P$ be such that 
\[
(A+BK)^TP(A+BK) \leq \rho^2P
\]
holds, where $\rho$ denotes the spectral radius of $A+BK$, such a matrix can be found using semi-definite programming.
%
To see that $\E_k$ grows exponentially let $\W\subseteq\B_P(r)$ then
%
\begin{multline*}
  \bigoplus_{i=0}^{k-1}(A+BK)^i\W \subseteq \bigoplus_{i=0}^{k-1}(A+BK)^i\B_P(r)\\
  \subseteq\bigoplus_{i=0}^{k-1}\B_P(\rho^i r) = \B_P\biggl(\sum_{i=0}^{k-1}\rho^i r\biggr)\subseteq\B_P\Bigl(\frac{r}{1-\rho}\Bigr) .
\end{multline*}
%
It follows that the subtrahend in square brackets on the RHS of (\ref{eq:Ek:subtract}) is bounded for all $k$ by $\B_P\bigl(r / (1-\rho)\bigr)$.
%It follows that the RHS of (\ref{eq:Ek:subtract}) consists of an expanding minuend and a bounded subtrahend.
%
Therefore 
%$\E_k$ expands exponentially. Hence 
the iteration (\ref{eq:MRPI:sequence}) must either yield $X_N = \emptyset$ for finite $N$
(in which case $X^\infty=\emptyset$) or,
since $X_{d-1}$ is bounded and $\E_k$ expands exponentially, there must exist a finite $N$ such that $X_{N}\cap\E_{N+1}=X_N$ and hence $X_N=X^\infty$.
%
\epf

@@

% For the same setup~\eqref{eq:example:system:MRPI} we approximate the guaranteed 3-step controllable set $\C_3(\T)$, where $\T=X^\infty$.
% %
% Again the result illustrated in Figure~\ref{fig:n:step:controllable:set} can be reproduced using different initial values although the Hessian at the maximiser has a non-trivial nullspace.
%
For the same system and constraints (\ref{eq:example:system:MRPI})-(\ref{eq:example:pconstriaint}) we approximate the guaranteed 3-step controllable set $\C_3(\T)$, with $\T=X^\infty$,
%
by solving (\ref{seq:optimisation:n:step:precise}a-d) for $C_1(X^\infty)$, $C_2(X^\infty)$, $C_3(X^\infty)$, where $X^\infty$ is the guaranteed positively invariant set computed via (\ref{seq:optimisation:MRPI:precise}a-d).
%
Again the results illustrated in Figure~\ref{fig:n:step:controllable:set} can be reproduced using different initial values even though the Hessian at the maximiser has a non-trivial nullspace. 
%
The figure also shows the controllable sets that are obtained, for the same target set (i.e.~$\T=X^\infty$), with a fixed set $\V^\prime$ which was computed using the sample based approach of~\citet{Zhang2015} by solving~(\ref{eq:comparison:set}a-b). 
%
Clearly the high level of sub-optimality in this choice of $\V^\prime$, which is a consequence of the requirement for a high level of confidence of satisfaction of the chance constraint, translates to sub-optimality in the computed sets $C_n(X^\infty)$.
\textcolor{red}{Did we not say that 5 sentences ago?}
%
% For the same system and constraints (\ref{eq:example:system:MRPI})-(\ref{eq:example:pconstriaint}) we approximate the guaranteed 3-step controllable set $\C_3(\T)$, where $\T=\{x:\norm{x}_\infty\leq 2\}$
% %
% by solving (\ref{seq:optimisation:n:step:set:abstract}a-c) for $C_1(\T)$, $C_2(\T)$, $C_3(\T)$.
% %
% Again the result illustrated in Figure~\ref{fig:n:step:controllable:set} is reproduced using different initial values although the Hessian at the maximiser has a non-trivial nullspace.
% %

>>>>

\title{Maximising the guaranteed feasible set for stochastic MPC with chance constraints}
%\title{Maximising the guaranteed feasible set for uncertain MPC schemes with chance constraints}%\thanksref{footnoteinfo}} 
% Title, preferably not more than 10 words.

@@

\begin{keyword}                           % Five to ten keywords,  
Robust control; chance constraints;  invariant sets; stochastic MPC. 
%Robust control; chance constraints; stochastic MPC; positively invariant sets.
\end{keyword}                             % keyword list or with the 
                                          % help of the Automatica 
                                          % keyword wizard

@@

\vspace{0.5\baselineskip}
\begin{thm}\label{thm2}
Assume that $K$ is chosen so that $\rho < 1$, where $\rho$ is the spectral radius of $A+BK$. Also let $\Gamma$ be a matrix such that $\Gamma x\leq\bfa{1}$ and $-\Gamma x\leq\bfa{1}$ for all $x\in X_0$ and let $\bigl((A+BK),\Gamma\bigr)$ be observable, then the iteration~\eqref{eq:MRPI:sequence} %terminates after a finite number, $N$, of iterations, such that 
yields $X_{k+1}=X_k$ for all $k\geq N$ and hence $X_k=X^\infty$ for some finite integer $N$.
\end{thm}
%
The matrix~$\Gamma$ is introduced to simplify  analysis of the iteration~(\ref{eq:MRPI:sequence}). Note that the rows of $\Gamma$ can include~$E_i$ and~$F_iK$, but $\Gamma$ need not contain all hyperplanes supporting~$X_0$ (consider for example the case of asymmetrical constraints).
%
\\[1em]
%
\bpf
%
The observability of the pair $\bigl((A+BK),\Gamma\bigr)$ implies that $X_{d-1}$ is compact, since 
\begin{align*}
X_{d-1} 
&\subseteq\bigcap_{k\leq d-1}(A+BK)^{-k} X_0\\
&\subseteq \Bigl\{x:\pm\Gamma x\leq\bfa{1}\wedge\dots\wedge\pm\Gamma(A+BK)^{d-1} x\leq\bfa{1} \Bigr\}\\
& = \bigl\{x:\pm\Gamma \Obs x\leq \bfa{1}\bigr\}
\end{align*}
where $\Obs$ is the (full rank) observability matrix.

Let~$P$ be such that 
\[
(A+BK)^TP(A+BK) \leq \rho^2P
\]
holds (a suitable matrix $P$ can be found using semi-definite programming).
%, where $\rho$ denotes the spectral radius of $A+BK$, 
%such a matrix can be found using semi-definite programming.
%
To see that $\E_k$ grows exponentially let $\W\subseteq\B_P(r)$ then
%
\begin{multline*}
  \bigoplus_{i=0}^{k-1}(A+BK)^i\W \subseteq \bigoplus_{i=0}^{k-1}(A+BK)^i\B_P(r)\\
  \subseteq\bigoplus_{i=0}^{k-1}\B_P(\rho^i r) = \B_P\biggl(\sum_{i=0}^{k-1}\rho^i r\biggr)\subseteq\B_P\Bigl(\frac{r}{1-\rho}\Bigr) .
\end{multline*}
%
It follows that the subtrahend in square brackets on the RHS of (\ref{eq:Ek:subtract}) is bounded for all $k$ by $\B_P\bigl(r / (1-\rho)\bigr)$.
%It follows that the RHS of (\ref{eq:Ek:subtract}) consists of an expanding minuend and a bounded subtrahend.
%
Therefore 
%$\E_k$ expands exponentially. Hence 
the iteration (\ref{eq:MRPI:sequence}) must either yield $X_N = \emptyset$ for finite $N$
(in which case $X^\infty=\emptyset$) or,
since $X_{d-1}$ is bounded and $\E_k$ expands exponentially, there must exist a finite $N$ such that $X_{N}\cap\E_{N+1}=X_N$ and hence $X_N=X^\infty$.
%
\epf

@@

% For the same setup~\eqref{eq:example:system:MRPI} we approximate the guaranteed 3-step controllable set $\C_3(\T)$, where $\T=X^\infty$.
% %
% Again the result illustrated in Figure~\ref{fig:n:step:controllable:set} can be reproduced using different initial values although the Hessian at the maximiser has a non-trivial nullspace.
%
For the same system and constraints (\ref{eq:example:system:MRPI})-(\ref{eq:example:pconstriaint}) we approximate the guaranteed 3-step controllable set $\C_3(\T)$, with $\T=X^\infty$,
%
by solving (\ref{seq:optimisation:n:step:precise}a-d) for $C_1(X^\infty)$, $C_2(X^\infty)$, $C_3(X^\infty)$, where $X^\infty$ is the guaranteed positively invariant set computed via (\ref{seq:optimisation:MRPI:precise}a-d).
%
Again the results illustrated in Figure~\ref{fig:n:step:controllable:set} can be reproduced using different initial values even though the Hessian at the maximiser has a non-trivial nullspace. 
%
The figure also shows the controllable sets that are obtained, for the same target set (i.e.~$\T=X^\infty$), with a fixed set $\V^\prime$ which was computed using the sample based approach of~\citet{Zhang2015} by solving~(\ref{eq:comparison:set}a-b). 
%
Clearly the high level of sub-optimality in this choice of $\V^\prime$, which is a consequence of the requirement for a high level of confidence of satisfaction of the chance constraint, translates to sub-optimality in the computed sets $C_n(X^\infty)$.
%\textcolor{red}{Did we not say that 5 sentences ago?}
%
% For the same system and constraints (\ref{eq:example:system:MRPI})-(\ref{eq:example:pconstriaint}) we approximate the guaranteed 3-step controllable set $\C_3(\T)$, where $\T=\{x:\norm{x}_\infty\leq 2\}$
% %
% by solving (\ref{seq:optimisation:n:step:set:abstract}a-c) for $C_1(\T)$, $C_2(\T)$, $C_3(\T)$.
% %
% Again the result illustrated in Figure~\ref{fig:n:step:controllable:set} is reproduced using different initial values although the Hessian at the maximiser has a non-trivial nullspace.
% %
